Meta-analysis of fungicide application timing experiments for powdery mildew management

### 2020-03-01 01_Meta-analysis_experiments.Rmd
Correct table so one line per trial

kable(
   PM.dat %>%
      group_by(
         trial_ref,
         year,
         location,
         trial_design,
         replicates,
         planting_date,
         emergence_date,
         first_sign_disease
      ) %>%
      summarise(treatments = length(n_treatment)),
   caption = "Description of Experiments"
)  %>%
   kable_styling(fixed_thead = TRUE, full_width = TRUE) %>%
   scroll_box(width = "900px", height = "500px")
```

>>>>

kable(
   PM.dat %>%
      group_by(
         trial_ref,
      ) %>%
      summarise(year = unique(year),
                location = unique(location),
                mean_treat_replicates = mean(replicates),
                planting_date = unique(planting_date),
                first_sign_disease = unique(first_sign_disease),
                treatments = length(n_treatment)),
   caption = "Description of Experiments"
)  %>%
   kable_styling(fixed_thead = TRUE, full_width = TRUE) %>%
   scroll_box(width = "900px", height = "500px")
```
